Supp mat: time series paper

### 2017-06-14 writing/supp_mat_draft.Rmd
cleaned up code for supp mat

Our model with trend strength, autocorrelation, variance, and generation length accounted for `r round(R2_fullmodel,2)`% of the variation in the minimum time required. However, we also found trend strength and variance to be strongly correlated with one another. Therefore, we ran two additional models with either trend strength or variance, but not both together. This resulted in lower explained deviance (analogue to $R^2$) of `r round(R2_no_variance,2)`% and `r round(R2_no_trend,2)`%, respectively.

@@

@@

In the main text, we examined the minimum time required to identify a trend in abundance via linear regression. This approach allowed us to identify increases or decreases, but a linear model may not always be a good fit. Generalized additive models (GAMs) are more general than general linear models and allow more flexible. GAMs are models where a response variable depends on unknown smooth functions of explanatory variables. GAMs, therefore, can identify relationships between response variables and explantory variables that are non-linear and perhaps more complicated. The downsite of GAMs...

>>>>

Our model with trend strength, autocorrelation, variance, and generation length accounted for `r round(R2_fullmodel,2)`% of the variation in the minimum time required (Table \ref{table:model_output}). However, we also found trend strength and variance to be strongly correlated with one another. Therefore, we ran two additional models with either trend strength or variance, but not both together. This resulted in lower explained deviance (analogue to $R^2$) of `r round(R2_no_variance,2)`% and `r round(R2_no_trend,2)`%, respectively.

@@

### Simulations with more complicated population model

In the main text, we showed how a simple population model could be simulated repeatidly to estimate the power obtained with time series of increasing length. The model in the main text simulated linear population growth with only a slope coefficient, y-intercept, and noise parameter required. This model is purely phenemilogical and does not include any species life history. Here, we use the same routine as the main text, but simulate from a more biologically-realistic population model, the (MODEL NAME HERE):

  \begin{equation}
    y = x
  \end{equation}

We simulate this model repetively for different lengths of time series. Statistical power is the fraction of time series of a set length that showed signicant trends in abundance, given a true trend in abundance. *How do I determine significance here? Through linear regression again, or do I look at non-zero estimation of the parameter values?*

### Empirical approach with more complicated population model (use model similar to de Valpine work?)

@@

In the main text, we examined the minimum time required to identify a trend in abundance via linear regression. This approach allowed us to identify increases or decreases, but a linear model may not always be a good fit. Generalized additive models (GAMs) are more general than general linear models and allow more flexible. GAMs are models where a response variable depends on unknown smooth functions of explanatory variables. GAMs, therefore, can identify relationships between response variables and explantory variables that are non-linear and perhaps more complicated. The downside of GAMs is they typically require more data and are also prone to overfitting (citations).

### 2017-06-14 writing/supp_mat_draft.tex
cleaned up code for supp mat

Our model with trend strength, autocorrelation, variance, and generation
length accounted for 72.55\% of the variation in the minimum time
required. However, we also found trend strength and variance to be
strongly correlated with one another. Therefore, we ran two additional
models with either trend strength or variance, but not both together.
This resulted in lower explained deviance (analogue to \(R^2\)) of
53.08\% and 45.04\%, respectively.

@@

@@

In the main text, we examined the minimum time required to identify a
trend in abundance via linear regression. This approach allowed us to
identify increases or decreases, but a linear model may not always be a
good fit. Generalized additive models (GAMs) are more general than
general linear models and allow more flexible. GAMs are models where a
response variable depends on unknown smooth functions of explanatory
variables. GAMs, therefore, can identify relationships between response
variables and explantory variables that are non-linear and perhaps more
complicated. The downsite of GAMs\ldots{}

>>>>

Our model with trend strength, autocorrelation, variance, and generation
length accounted for 72.55\% of the variation in the minimum time
required (Table \ref{table:model_output}). However, we also found trend
strength and variance to be strongly correlated with one another.
Therefore, we ran two additional models with either trend strength or
variance, but not both together. This resulted in lower explained
deviance (analogue to \(R^2\)) of 53.08\% and 45.04\%, respectively.

@@

\subsubsection{Simulations with more complicated population
model}\label{simulations-with-more-complicated-population-model}

In the main text, we showed how a simple population model could be
simulated repeatidly to estimate the power obtained with time series of
increasing length. The model in the main text simulated linear
population growth with only a slope coefficient, y-intercept, and noise
parameter required. This model is purely phenemilogical and does not
include any species life history. Here, we use the same routine as the
main text, but simulate from a more biologically-realistic population
model, the (MODEL NAME HERE):

\begin{equation}
    y = x
  \end{equation}

We simulate this model repetively for different lengths of time series.
Statistical power is the fraction of time series of a set length that
showed signicant trends in abundance, given a true trend in abundance.
\emph{How do I determine significance here? Through linear regression
again, or do I look at non-zero estimation of the parameter values?}

\subsubsection{Empirical approach with more complicated population model
(use model similar to de Valpine
work?)}\label{empirical-approach-with-more-complicated-population-model-use-model-similar-to-de-valpine-work}

@@

In the main text, we examined the minimum time required to identify a
trend in abundance via linear regression. This approach allowed us to
identify increases or decreases, but a linear model may not always be a
good fit. Generalized additive models (GAMs) are more general than
general linear models and allow more flexible. GAMs are models where a
response variable depends on unknown smooth functions of explanatory
variables. GAMs, therefore, can identify relationships between response
variables and explantory variables that are non-linear and perhaps more
complicated. The downside of GAMs is they typically require more data
and are also prone to overfitting (citations).
